Detection of defects in additive manufacturing from a single x-ray projection using the empirical null filter

### 2019-08-27 reports/paper1/paper.tex
Revise paper

X-ray projections were obtained using the \emph{Nikon XT H LC 225/320} x-ray CT scanner \emph{(Nikon Metrology, UK)}. The \SI{225}{\kilo\volt} source was used with a $\SI{2000}{\pixel}\times\SI{2000}{\pixel}$ \emph{Perkin Elmer} detector consisting of \SI{200}{\micro\metre} pixels, separated by a distance of \SI{1870}{\milli\metre}. The sample was placed on the manipulator, positioned to obtain a $5.7\times$ magnification resulting in an equivalent pixel size of \SI{35}{\micro\metre}. A voltage of \SI{80}{\kilo\volt} was used with a power of \SI{20}{\watt} resulting in a spot size of \SI{20}{\micro\metre} such that penumbra effects \citep{kueh2016modelling} were negligible. 20 greyscale projections were acquired at an exposure time of \SI{500}{\milli\second}. A shading correction \citep{seibert1998flat} was applied to each projection using 20 greyscale projections, with powers \SI{0}{\kilo\volt}, \SI{5}{\kilo\volt}, \SI{10}{\kilo\volt}, \SI{15}{\kilo\volt} and \SI{20}{\kilo\volt}, to remove intensity influences and variations in pixels of the detector.

19 randomly selected projections, of the test sample, were held out. The remaining projection was used to compare with a simulated projection, obtained using \emph{aRTist} \citep{bellon2012radiographic, bellon2007artist, jaenisch2008artist}. \emph{aRTist} can simulate projections of the sample given the specifications of the CT apparatus, such as the x-ray source and the x-ray detector, and the
CAD of the sample \citep{bellon2011simulation, deresch2012simulating}. \emph{aRTist} was used to obtain a simulation projection as if the voids were not there. Numerical methods were used to align the simulated projection to the obtained projection. The same shading correction was applied to the simulated projection, but instead using a flat black image and a simulated greyscale projections.

>>>>

X-ray projections were obtained using the \emph{Nikon XT H LC 225/320} x-ray CT scanner \emph{(Nikon Metrology, UK)}. The \SI{225}{\kilo\volt} source was used with a $\SI{2000}{\pixel}\times\SI{2000}{\pixel}$ \emph{Perkin Elmer} detector consisting of \SI{200}{\micro\metre} pixels, separated by a distance of \SI{1870}{\milli\metre}. The sample was placed on the manipulator, positioned to obtain a $5.7\times$ magnification resulting in an equivalent pixel size of \SI{35}{\micro\metre}. A voltage of \SI{80}{\kilo\volt} was used with a power of \SI{20}{\watt} resulting in a spot size of \SI{20}{\micro\metre} such that penumbra effects \citep{kueh2016modelling} were negligible. 20 replicate greyscale projections were acquired using an exposure time of \SI{500}{\milli\second} and the following powers: \SI{0}{\kilo\volt}, \SI{5}{\kilo\volt}, \SI{10}{\kilo\volt}, \SI{15}{\kilo\volt} and \SI{20}{\kilo\volt}. A shading correction \citep{seibert1998flat} was applied to each projection of the test sample using the greyscale projections to remove intensity influences and variations in pixels of the detector.

19 randomly selected projections, of the test sample, were held out. The remaining projection was used to compare with a simulated projection, obtained using \emph{aRTist} \citep{bellon2012radiographic, bellon2007artist, jaenisch2008artist}. \emph{aRTist} can simulate projections of the sample given the specifications of the CT apparatus, such as the x-ray source and the x-ray detector, and the
CAD of the sample \citep{bellon2011simulation, deresch2012simulating}. \emph{aRTist} was used to obtain a simulation projection as if the voids were not there. Numerical methods were used to align the simulated projection to the obtained projection. The same shading correction was applied to the simulated projection, but instead using a flat black image and simulated greyscale projections.
